---
---
title: "Recommendation sys"
output: pdf_document
---

date: "2024-12-10"
---

```{r}
#Libraries
library(sf)
library(ggplot2)
library(tmap)
library(dplyr)
library(dplyr)
library(janitor)    
library(lubridate)
library(tidyr)
library(htmltools)
```

#NEW TERRITORIES MAP
```{r}
#hongkong shapefile
hk_districts <- st_read("/Users/apple/Downloads/Hong_Kong_18_Districts_3574690825663895789")
#map of all hongkong districts
ggplot(data = hk_districts) +
  geom_sf(aes(fill =ENAME)) +  
  labs(title = "Map of all Districts in Hong Kong",
       fill = "District") +
  theme_minimal()
```
```{r}
# Districts in NTE and NTW regions
nte_districts <- c("SHA TIN", "TAI PO", "NORTH", "SAI KUNG") 
ntw_districts <- c("KWAI TSING", "TSUEN WAN", "TUEN MUN", "YUEN LONG")
# Subsetting the districts in NTE and NTW
nte_districts_data <- hk_districts[hk_districts$ENAME %in% nte_districts, ]
ntw_districts_data <- hk_districts[hk_districts$ENAME %in% ntw_districts, ]

# Assigning colors to the NTE and NTW districts
nte_colors <- c("#4CAF50", "#2196F3", "#00BCD4", "#FF9800")
ntw_colors <- c("#673AB7", "#E91E63", "#FFC107", "#FFC107")
nte_districts_data$color <- nte_colors
ntw_districts_data$color <- ntw_colors

# New territory map
ggplot() +
  geom_sf(data = nte_districts_data, aes(fill = color)) +
  geom_sf(data = ntw_districts_data, aes(fill = color)) +
  geom_sf_text(data = nte_districts_data, aes(label = ENAME), size = 3, color = "black", fontface = "bold") +
  geom_sf_text(data = ntw_districts_data, aes(label = ENAME), size = 3, color = "black", fontface = "bold") +
  scale_fill_identity() +
  labs(title = "Map of NTE and NTW Districts in Hong Kong") +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5),
    axis.text = element_blank(),
    axis.ticks = element_blank()
  )
```

```{r load-data, include=TRUE}
#DATA CLEANING
#Check duplicates
#Duplicate Rows in Each Dataset
#install.packages("openxlsx")
library(openxlsx)
Traffic_data<- read.xlsx("/Users/apple/Downloads/Traffic.xlsx")
Housing_prices <- read.csv("/Users/apple/Downloads/Housing prices.csv")
School_data <- read.xlsx("/Users/apple/Downloads/School data.xlsx")
Census_data <- read.csv("/Users/apple/Downloads/Census and Social information.csv")
Housing_parking <- read.csv("/Users/apple/Downloads/Housing parking.csv")
sum(duplicated(Housing_prices))  # Count of duplicate rows in Housing_prices
sum(duplicated(School_data))    # Count of duplicate rows in School_data
sum(duplicated(Census_data))    # Count of duplicate rows in Census_data
sum(duplicated(Traffic_data))   # Count of duplicate rows in Traffic_data

#There are no duplicates```{r}
```
```{r}
#MISSING VALUES
# Check for missing values and count them in each dataset
sum(is.na(Housing_prices))  
sum(is.na(School_data))     
sum(is.na(Census_data))     
sum(is.na(Traffic_data)) 
#There are no missing values
```
```{r}
#Normalizing categorical variables
#SCHOOL DATA

#Assign SESSION_RANK Based on Session Type
School_data <- School_data %>%
  mutate(SESSION_RANK = case_when(
    SESSION == "WHOLE DAY" ~ 10,
    SESSION == "P.M." ~ 7,
    SESSION == "A.M." ~ 4,
    SESSION == "EVENING" ~ 2,
    TRUE ~ 0  # In case there are any unexpected values
  ))
```

```{r}
# View the updated SESSION_RANK column
table(School_data$SESSION_RANK)
#English category rank of schools
#Assign RANK Based on English Category
School_data <- School_data %>%
  mutate(ENGLISH_CATEGORY_RANK = case_when(
    `ENGLISH.CATEGORY` %in% c("International Schools (Primary)", "International Schools (Secondary)") ~ 10,
    `ENGLISH.CATEGORY` %in% c("English Schools Foundation (Primary)", "English Schools Foundation (Secondary)") ~ 9,
    `ENGLISH.CATEGORY` == "Government Secondary Schools" ~ 8,
    `ENGLISH.CATEGORY` == "Aided Secondary Schools" ~ 7,
    `ENGLISH.CATEGORY` == "Direct Subsidy Scheme Secondary Schools" ~ 6,
    `ENGLISH.CATEGORY` == "Private Secondary Schools (Day/Evening)" ~ 5,
    `ENGLISH.CATEGORY` == "Aided Primary Schools" ~ 4,
    `ENGLISH.CATEGORY` == "Government Primary Schools" ~ 3,
    `ENGLISH.CATEGORY` %in% c("Kindergartens", "Kindergarten-cum-child Care Centres") ~ 1,
    TRUE ~ 0  # In case there are any unexpected values
  ))
head(School_data)

```

```{r}
#ENGLISH_CATEGORY_RANK column
table(School_data$ENGLISH_CATEGORY_RANK)
#Rank based on finance type
#Assign RANK Based on Finance Type ---
School_data <- School_data %>%
  mutate(FINANCE_TYPE_RANK = case_when(
    `FINANCE.TYPE` == "ENGLISH SCHOOLS FOUNDATION" ~ 10,
    `FINANCE.TYPE` == "DIRECT SUBSIDY SCHEME" ~ 9,
    `FINANCE.TYPE` == "AIDED" ~ 8,
    `FINANCE.TYPE` == "GOVERNMENT" ~ 7,
    `FINANCE.TYPE` == "PRIVATE" ~ 5,
    `FINANCE.TYPE` == "PRIVATE INDEPENDENT SCH SCHEME" ~ 3,
    `FINANCE.TYPE` == "CAPUT" ~ 1,
    TRUE ~ 0  
  ))

# FINANCE_TYPE_RANK column
table(School_data$FINANCE_TYPE_RANK)

# Assigning RANK Based on School Level 
School_data <- School_data %>%
  mutate(SCHOOL_LEVEL_RANK = case_when(
    `SCHOOL.LEVEL` == "SECONDARY" ~ 10,
    `SCHOOL.LEVEL` == "PRIMARY" ~ 8,
    `SCHOOL.LEVEL` == "KINDERGARTEN-CUM-CHILD CARE CENTRES" ~ 6,
    `SCHOOL.LEVEL` == "KINDERGARTEN" ~ 5,
    TRUE ~ 0  
  ))
```
```{r}
# SCHOOL_LEVEL_RANK column
table(School_data$SCHOOL_LEVEL_RANK)
#districts for NTE and NTW
nte_ntw_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH", "YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")

# Filtering School_data to keep only rows where DISTRICT is in NTE or NTW
School_data <- School_data %>%
  filter(DISTRICT %in% nte_ntw_districts)

# Checking the filtered data
table(School_data$DISTRICT)
```
```{r}
#Column for region
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH
")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")

School_data <- School_data %>%
  mutate(REGION = case_when(
    DISTRICT %in% nte_districts ~ "NTE",  # New Territories East
    DISTRICT %in% ntw_districts ~ "NTW",  # New Territories West
    TRUE ~ "Other"  
  ))
#School rank
# Combining all the individual ranks to generate a total score for each school
colnames(School_data)
School_data <- School_data %>%
  mutate(
    TOTAL_RANK = SESSION_RANK + ENGLISH_CATEGORY_RANK + FINANCE_TYPE_RANK + SCHOOL_LEVEL_RANK
  )

#  Ranking the schools based on the total rank
School_data <- School_data %>%
  arrange(desc(TOTAL_RANK)) %>%
  mutate(RANK = row_number())

#top 10 schools based on the rank
top_schools <- School_data %>%
  select(`ENGLISH.NAME`, DISTRICT, REGION, RANK) %>%  
  slice_head(n = 50)
# View the top 3 schools
head(top_schools, n = 50)

```
```{r}
##Housing parking
colnames(Housing_parking)
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")
Housing_parking <- Housing_parking %>%
  mutate(
    Total_Parking = `For.Vehicles.Other.Than.Medium.and.Heavy.Goods.Vehicles..Buses..Motor.Cycles.and.Pedal.Cycles.` + 
      `For.Goods.Vehicles` + 
      `For.Coaches`,  # Calculate total parking spaces
    REGION = case_when(
      District %in% nte_districts ~ "NTE",   
      District %in% ntw_districts ~ "NTW",   
      TRUE ~ "Other"  # Assign "Other" for districts not in NTE or NTW
    )
  ) %>%
  group_by(District, REGION) %>%  # Group by District and REGION
  summarise(
    Total_Parking = sum(Total_Parking, na.rm = TRUE),  # Sum parking spaces by district and region
    .groups = "drop"  # Remove grouping after summarization
  ) %>%
  arrange(REGION, desc(Total_Parking))  # Sort by REGION and then by total parking

# View the result
print(Housing_parking)
```

```{r}
####################Traffic data
colnames(Traffic_data)
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")

# Add REGION column based on districts
Traffic <- Traffic_data %>%
  mutate(REGION = case_when(
    District %in% nte_districts ~ "NTE",
    District %in% ntw_districts ~ "NTW",
    TRUE ~ "Other"
  ))

# Summarize total traffic (including all visitors) by District and Control Point
Traffic_summary <- Traffic %>%
  group_by(District, "Control Point", REGION) %>%
  summarise(
    Total_HongKong_Residents = sum(`Hong.Kong.Residents`, na.rm = TRUE),
    Total_Mainland_Visitors = sum(`Mainland.Visitors`, na.rm = TRUE),
    Total_Other_Visitors = sum(`Other.Visitors`, na.rm = TRUE),
    Total_Traffic = sum(Total, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(REGION, desc(Total_Traffic))  

# Summarize total traffic (arrivals and departures) by District
Traffic_summary <- Traffic %>%
  mutate(REGION = case_when(
    District %in% nte_districts ~ "NTE",
    District %in% ntw_districts ~ "NTW",
    TRUE ~ "Other"
  )) %>%
  group_by(District, REGION) %>%
  summarise(
    Total_HongKong_Residents_Arrivals = sum(`Hong.Kong.Residents`[`Arrival./.Departure` == "Arrival"], na.rm = TRUE),
    Total_HongKong_Residents_Departures = sum(`Hong.Kong.Residents`[`Arrival./.Departure` == "Departure"], na.rm = TRUE),
    Total_Mainland_Visitors_Arrivals = sum(`Mainland.Visitors`[`Arrival./.Departure` == "Arrival"], na.rm = TRUE),
    Total_Mainland_Visitors_Departures = sum(`Mainland.Visitors`[`Arrival./.Departure` == "Departure"], na.rm = TRUE),
    Total_Other_Visitors_Arrivals = sum(`Other.Visitors`[`Arrival./.Departure` == "Arrival"], na.rm = TRUE),
    Total_Other_Visitors_Departures = sum(`Other.Visitors`[`Arrival./.Departure` == "Departure"], na.rm = TRUE),
    Total_Arrivals = sum(Total[`Arrival./.Departure` == "Arrival"], na.rm = TRUE),
    Total_Departures = sum(Total[`Arrival./.Departure` == "Departure"], na.rm = TRUE),
    Total_Traffic = sum(Total, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(REGION, desc(Total_Traffic))  # Sort by REGION and then by total traffic
# View the result
print(Traffic_summary)
```
```{r}
###############
###############Housing prices
# Reshape the dataset from wide to long format
Housing_long <- Housing_prices %>%
  pivot_longer(cols = `KWAI.TSING`:`YUEN.LONG`,
               names_to = "District", 
               values_to = "Housing_Price") %>%
  arrange(Year, District)

# View the reshaped dataset
print(Housing_long)
```

```{r}
# Define NTE and NTW districts
colnames(Housing_long)
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")

# Add a column for REGION
Housing_long <- Housing_long %>%
  mutate(REGION = case_when(
    District %in% nte_districts ~ "NTE",   
    District %in% ntw_districts ~ "NTW",   
    TRUE ~ "Other"  
  ))

ggplot(Housing_long, aes(x = Year, y = Housing_Price, color = REGION, group = District)) +
  geom_line(size = 1.2) +  # Bold lines
  geom_text(data = Housing_long %>%
              group_by(District) %>%
              filter(Year == max(Year)),  # Filter to get last year for each district
            aes(label = District), 
            vjust = -0.5, size = 3, check_overlap = TRUE) +
  labs(title = "Housing Price Trends by District (1999-2023)", 
       x = "Year", 
       y = "Housing Price (HKD)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

# Define the districts for NTE and NTW
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")

# average housing price for each district, region, and rank by price
Housing_summary <- Housing_prices %>%
  pivot_longer(cols = starts_with("KWAI.TSING"):starts_with("YUEN.LONG"),
               names_to = "District", 
               values_to = "Housing_Price") %>%
  group_by(District) %>%
  summarise(Average_Housing_Price = mean(Housing_Price, na.rm = TRUE)) %>%
  mutate(REGION = case_when(
    District %in% nte_districts ~ "NTE",   
    District %in% ntw_districts ~ "NTW",   
    TRUE ~ "Other"  
  )) %>%
  arrange(Average_Housing_Price)  # Sorting by Average_Housing_Price (ascending)

# View the result
print(Housing_summary)
```

```{r}
##################Census and social  information
# Define the districts for NTE and NTW in capital letters
nte_districts <- c("SAI KUNG", "SHA TIN", "TAI PO", "NORTH")
ntw_districts <- c("YUEN LONG", "KWAI TSING", "TSUEN WAN", "TUEN MUN")
colnames(Census_data)


# Add the REGION column to Census_data, considering the capitalized 'DISTRICT' column name
Census_data <- Census_data %>%
  mutate(REGION = case_when(
    `DISTRICT` %in% nte_districts ~ "NTE",   
    `DISTRICT` %in% ntw_districts ~ "NTW",   
    TRUE ~ "Other"  
  ))


#Friendly neighbourhood is the one with many children
# age distribution visualization
# age group data to compare across districts
Census_data %>%
  gather(key = "Age_Group", value = "Population", "X..15", "X15...24", "X25...44", "X45...64", "X65.") %>%
  ggplot(aes(x = DISTRICT, y = Population, fill = Age_Group)) +
  geom_bar(stat = "identity", position = "stack") +
  labs(title = "Age Group Distribution by District", x = "District", y = "Population")

```

```{r}
#Education
# percentage of population with post-secondary education
Census_data %>%
  mutate(Post_Secondary_Percentage = (`Post.secondary..Degree.course` / `Total.population`) * 100) %>%
  ggplot(aes(x = DISTRICT, y = Post_Secondary_Percentage, fill = REGION)) +
  geom_bar(stat = "identity") +
  labs(title = "Post-Secondary Education Percentage by District", x = "District", y = "Percentage (%)")

```

```{r}
#working population and employers
# Plot of working population and employers by district
ggplot(Census_data, aes(x = DISTRICT, y = `Working.population`, fill = REGION)) +
  geom_bar(stat = "identity") +
  labs(title = "Working Population by District", x = "District", y = "Working Population")
```

```{r}
# social dynamics
# Plot divorce rates by district
ggplot(Census_data, aes(x = DISTRICT, y = Divorces, fill = REGION)) +
  geom_bar(stat = "identity") +
  labs(title = "Divorce Rates by District", x = "District", y = "Divorces")
```
```{r}
Census_data <- Census_data %>%
  mutate(
    Post_Secondary_Percentage = (`Post.secondary..Degree.course` / `Total.population`) * 100,
    Rank_Score = (`Working.population` * 0.6) + (Post_Secondary_Percentage * 0.4)
  ) %>%
  arrange(desc(Rank_Score))
# Compare the number of working population in NTE and NTW
ggplot(Census_data, aes(x = REGION, y = `Working.population`, fill = REGION)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(title = "Working Population by Region (NTE vs NTW)", x = "Region", y = "Working Population")
```
```{r}
####Cluster analysis
# Select relevant columns for clustering
clustering_data <- Census_data %>%
  select(`Total.population`, `Post.secondary..Degree.course`, `Working.population`, Divorces)

# Normalize data for clustering
clustering_data_scaled <- scale(clustering_data)

# Perform k-means clustering (you can experiment with k)
set.seed(123)
kmeans_result <- kmeans(clustering_data_scaled, centers = 3)

# Add cluster to the original data
Census_data$Cluster <- kmeans_result$cluster

# Visualize clustering
ggplot(Census_data, aes(x = `Working.population`, y = `Post.secondary..Degree.course`, color = as.factor(Cluster))) +
  geom_point() +
  labs(title = "Cluster Analysis of Districts", x = "Working Population", y = "Post-Secondary Education")
```

```{r}
#MERGE DATASET
# Standardizing column names for consistency
colnames(Census_data)[colnames(Census_data) == "DISTRICT"] <- "District"
colnames(Housing_parking)[colnames(Housing_parking) == "District"] <- "District"
colnames(Housing_long)[colnames(Housing_long) == "District"] <- "District"
colnames(Traffic)[colnames(Traffic) == "District"] <- "District"
colnames(School_data)[colnames(School_data) == "DISTRICT"] <- "District"
colnames(Census_data)[colnames(Census_data) == "District"] <- "District"


```

```{r}

# Function to calculate mode
get_mode <- function(x) {
  ux <- unique(na.omit(x))
  ux[which.max(tabulate(match(x, ux)))]
}

# Aggregating School_data by District
School_data_agg <- School_data %>%
  select(-c(ENGLISH.NAME, ENGLISH.ADDRESS, LONGITUDE, LATITUDE, EASTING, NORTHING, TELEPHONE, FAX.NUMBER, WEBSITE, RELIGION)) %>%
  group_by(District) %>%
  summarize(
    Avg_SCHOOL_NO = mean(as.numeric(SCHOOL.NO.), na.rm = TRUE), 
    Most_Common_ENGLISH_CATEGORY = get_mode(ENGLISH.CATEGORY),
    Avg_SESSION_RANK = mean(as.numeric(SESSION_RANK), na.rm = TRUE),
    Avg_ENGLISH_CATEGORY_RANK = mean(as.numeric(ENGLISH_CATEGORY_RANK), na.rm = TRUE),
    Avg_FINANCE_TYPE_RANK = mean(as.numeric(FINANCE_TYPE_RANK), na.rm = TRUE),
    Avg_SCHOOL_LEVEL_RANK = mean(as.numeric(SCHOOL_LEVEL_RANK), na.rm = TRUE),
    Avg_TOTAL_RANK = mean(as.numeric(TOTAL_RANK), na.rm = TRUE),
    Avg_RANK = mean(as.numeric(RANK), na.rm = TRUE),
    Most_Common_STUDENTS_GENDER = get_mode(STUDENTS.GENDER),
    Most_Common_SESSION = get_mode(SESSION),
    Most_Common_FINANCE_TYPE = get_mode(FINANCE.TYPE),
    Most_Common_SCHOOL_LEVEL = get_mode(SCHOOL.LEVEL)
  )

# View the first few rows of the aggregated School_data
head(School_data_agg)

```


```{r}
# Merge step-by-step
merged_data <- Census_data %>%
  left_join(Housing_parking, by = "District")

gc() # Clear memory

merged_data <- merged_data %>%
  left_join(Housing_long, by = "District")

gc() # Clear memory

merged_data <- merged_data %>%
  left_join(Traffic, by = "District")

gc() # Clear memory

merged_data <- merged_data %>%
  left_join(School_data_agg, by = "District")

gc() # Clear memory
tail(merged_data)
```

```{r}
# View duplicated rows

duplicated_rows <- merged_data[duplicated(merged_data$District), ]
View(duplicated_rows)

#  remove duplicates
#merged_data <- merged_data %>% distinct()

# Aggregate School Data 
#merged_data <- merged_data %>%
  #group_by(District) %>%
   #summarize(across(everything(), ~ if(is.numeric(.)) mean(., na.rm = TRUE) else first(.)))

# Check for missing values
colSums(is.na(merged_data))

# Visualize missing data
library(naniar)
#vis_miss(merged_data)  
# Impute missing values with the mean 
# Impute missing values for numerical columns with the mean
merged_data <- merged_data %>%
  mutate(
    Total_Parking = ifelse(is.na(Total_Parking), mean(Total_Parking, na.rm = TRUE), Total_Parking),
    Housing_Price = ifelse(is.na(Housing_Price), mean(Housing_Price, na.rm = TRUE), Housing_Price),
    Avg_SCHOOL_NO = ifelse(is.na(Avg_SCHOOL_NO), mean(Avg_SCHOOL_NO, na.rm = TRUE), Avg_SCHOOL_NO),
    Avg_SESSION_RANK = ifelse(is.na(Avg_SESSION_RANK), mean(Avg_SESSION_RANK, na.rm = TRUE), Avg_SESSION_RANK),
    Avg_ENGLISH_CATEGORY_RANK = ifelse(is.na(Avg_ENGLISH_CATEGORY_RANK), mean(Avg_ENGLISH_CATEGORY_RANK, na.rm = TRUE), Avg_ENGLISH_CATEGORY_RANK),
    Avg_FINANCE_TYPE_RANK = ifelse(is.na(Avg_FINANCE_TYPE_RANK), mean(Avg_FINANCE_TYPE_RANK, na.rm = TRUE), Avg_FINANCE_TYPE_RANK),
    Avg_SCHOOL_LEVEL_RANK = ifelse(is.na(Avg_SCHOOL_LEVEL_RANK), mean(Avg_SCHOOL_LEVEL_RANK, na.rm = TRUE), Avg_SCHOOL_LEVEL_RANK),
    Avg_TOTAL_RANK = ifelse(is.na(Avg_TOTAL_RANK), mean(Avg_TOTAL_RANK, na.rm = TRUE), Avg_TOTAL_RANK)
  )
# Function to get the mode
get_mode <- function(x) {
  uniq_x <- unique(x)
  uniq_x[which.max(tabulate(match(x, uniq_x)))]
}

# Impute missing values for categorical columns with the mode
merged_data <- merged_data %>%
  mutate(
    Most_Common_ENGLISH_CATEGORY = ifelse(is.na(Most_Common_ENGLISH_CATEGORY), get_mode(Most_Common_ENGLISH_CATEGORY), Most_Common_ENGLISH_CATEGORY),
    Most_Common_STUDENTS_GENDER = ifelse(is.na(Most_Common_STUDENTS_GENDER), get_mode(Most_Common_STUDENTS_GENDER), Most_Common_STUDENTS_GENDER),
    Most_Common_SESSION = ifelse(is.na(Most_Common_SESSION), get_mode(Most_Common_SESSION), Most_Common_SESSION),
    Most_Common_FINANCE_TYPE = ifelse(is.na(Most_Common_FINANCE_TYPE), get_mode(Most_Common_FINANCE_TYPE), Most_Common_FINANCE_TYPE),
    Most_Common_SCHOOL_LEVEL = ifelse(is.na(Most_Common_SCHOOL_LEVEL), get_mode(Most_Common_SCHOOL_LEVEL), Most_Common_SCHOOL_LEVEL)
  )
# Impute missing values for numerical columns with the mean
merged_data <- merged_data %>%
  mutate(
    Hong.Kong.Residents = ifelse(is.na(Hong.Kong.Residents), mean(Hong.Kong.Residents, na.rm = TRUE), Hong.Kong.Residents),
    Mainland.Visitors = ifelse(is.na(Mainland.Visitors), mean(Mainland.Visitors, na.rm = TRUE), Mainland.Visitors),
    Other.Visitors = ifelse(is.na(Other.Visitors), mean(Other.Visitors, na.rm = TRUE), Other.Visitors),
    Total = ifelse(is.na(Total), mean(Total, na.rm = TRUE), Total),
    Avg_SCHOOL_NO = ifelse(is.na(Avg_SCHOOL_NO), mean(Avg_SCHOOL_NO, na.rm = TRUE), Avg_SCHOOL_NO),
    Avg_SESSION_RANK = ifelse(is.na(Avg_SESSION_RANK), mean(Avg_SESSION_RANK, na.rm = TRUE), Avg_SESSION_RANK),
    Date = ifelse(is.na(Date), mean(Date, na.rm = TRUE), Date)  # If Date is numeric, else use mode for categorical
  )

# Function to get the mode (for categorical data)
get_mode <- function(x) {
  uniq_x <- unique(x)
  uniq_x[which.max(tabulate(match(x, uniq_x)))]
}

# Impute missing values for categorical columns with the mode
merged_data <- merged_data %>%
  mutate(
    REGION.x.x = ifelse(is.na(REGION.x.x), get_mode(REGION.x.x), REGION.x.x),
    REGION.y.y = ifelse(is.na(REGION.y.y), get_mode(REGION.y.y), REGION.y.y),
    Control.Point = ifelse(is.na(Control.Point), get_mode(Control.Point), Control.Point),
    Most_Common_ENGLISH_CATEGORY = ifelse(is.na(Most_Common_ENGLISH_CATEGORY), get_mode(Most_Common_ENGLISH_CATEGORY), Most_Common_ENGLISH_CATEGORY)
  )




colnames(merged_data) <- make.names(colnames(merged_data))  # Replaces spaces and symbols with dots

# Check data types
str(merged_data)

# Convert  columns
merged_data <- merged_data %>%
  mutate(
    Year = as.integer(Year),
    District = as.factor(District),
    Housing_Price = as.numeric(Housing_Price),
    Total_Parking = as.numeric(Total_Parking)
  )


print(head(merged_data))
```
```{r}
# Check missing values again
colSums(is.na(merged_data))

```

```{r}
#############EXPLORATORY DATA ANALYSIS
#Data Overview
str(merged_data)
dim(merged_data)

#chcek missing
colSums(is.na(merged_data))
#Summary statistics
summary(merged_data)

```

```{r}
#Univariate analysis
table(merged_data$REGION.y,merged_data$REGION.x)
barplot(table(merged_data$REGION.y,merged_data$REGION.x))
hist(merged_data$`Total.population`, main = "Total Population Distribution", xlab = "Total Population")
boxplot(merged_data$`Housing_Price`, main = "Housing Price Distribution", ylab = "Price")
#Outlier detection
boxplot(merged_data$Housing_Price, main = "Boxplot for Housing Prices")
#Bivariate Analysis
#Numerical vs numerical
plot(merged_data$`Housing_Price`, merged_data$`Total.population`, 
     main = "Housing Price vs Total Population", 
     xlab = "Housing Price", ylab = "Total Population")
cor(merged_data$Housing_Price, merged_data$`Total.population`, use = "complete.obs")
#correlation between housing price and totalpopulation=0.4719672

```

```{r}
#Categorical vs. Numerical:

#Boxplot of housing prices for each region
boxplot(Housing_Price ~ REGION.x, data = merged_data, 
        main = "Housing Prices by Region", 
        xlab = "Region", ylab = "Housing Price")
```
```{r}
# columns that are "constant" (have only one unique value excluding NA)
constant_cols <- sapply(merged_data, function(col) length(unique(na.omit(col))) == 1)

# Drop these constant columns
merged_data <- merged_data[, !constant_cols]

```


```{r}
#Multivariate Analysis
#Heatmap of correlations between numerical variables:
library(ggcorrplot)
num_data <- merged_data %>% select_if(is.numeric)
constant_cols <- sapply(num_data, function(x) sd(x, na.rm = TRUE) == 0)
constant_cols
num_data <- num_data[, !constant_cols]
corr_matrix <- cor(num_data, use = "complete.obs")
ggcorrplot(corr_matrix, lab = TRUE)

#Principal Component Analysis (PCA) for dimensionality reduction and pattern discovery:
library(FactoMineR)
pca_results <- PCA(merged_data %>% select_if(is.numeric), graph = TRUE)
```

```{r}
colnames(merged_data)
```

```{r}
#Key Insights and Visualization

ggplot(merged_data, aes(x = Housing_Price)) +
  geom_histogram(binwidth = 5000, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Housing Prices", x = "Housing_Price", y = "Frequency")
```

```{r}
#Interactive plot#s
library(plotly)
#plot_ly(merged_data, x = ~Housing_Price, y = ~Total.population, type = 'scatter', mode = 'markers')
```
```{r}
#Correlation analysis
# Calculate Pearson's correlation for relevant variables

# Calculate Pearson's correlation for relevant numeric variables
correlation_matrix <- cor(merged_data[c("Housing_Price", "Total.population", "Total", 
                                        "Total_Parking", "Post.secondary..Degree.course", 
                                        "Rank_Score", "Working.population", "Divorces", 
                                        "Hong.Kong.Residents", "Mainland.Visitors", 
                                        "Other.Visitors", "Avg_SCHOOL_NO", 
                                        "Avg_SESSION_RANK", "Avg_ENGLISH_CATEGORY_RANK", 
                                        "Avg_FINANCE_TYPE_RANK", "Avg_SCHOOL_LEVEL_RANK", 
                                        "Avg_TOTAL_RANK", "Avg_RANK")], 
                          use = "complete.obs")

# View the correlation matrix
print(correlation_matrix)

```

```{r}
#Visualize the correlation matrix

library(reshape2)
library(ggplot2)

# Reshape the correlation matrix for ggplot
correlation_melt <- melt(correlation_matrix)
ggplot(correlation_melt, aes(Var1, Var2, fill = value)) +
  geom_tile() + 
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) + 
  theme_minimal() + 
  labs(title = "Correlation Heatmap", x = "", y = "")

```

```{r}
#Statistical Tests
#t-test
#comparing house prices between New Territories East (NTE) and New Territories West (NTW).
# Perform t-test for house prices between NTE and NTW
colnames(Housing_long)
t_test_result <- t.test(Housing_Price ~REGION.x, data = merged_data)
print(t_test_result)
#If the p-value is less than 0.05, it suggests that the means between the two regions are significantly different
```
```{r}
#ANOVA
# ANOVA to compare house prices across different districts
anova_result <- aov(Housing_Price ~ District, data = merged_data)
summary(anova_result)
# ANOVA table
anova_table <- anova(anova_result)
print(anova_table)
colnames(merged_data)
##Linear regression
# Fit a linear regression model
# Fit a linear regression model 
model <- lm(Housing_Price ~ Hong.Kong.Residents + Mainland.Visitors + Avg_SCHOOL_LEVEL_RANK, data = merged_data)
summary(model)
# Diagnostic plots for the linear regression model
par(mfrow = c(2, 2))  # Set up a 2x2 plot grid
plot(model)
```

```{r}
#Chi-Square Test for Categorical Data
# Perform Chi-square test for Cluster vs REGION
chi_test <- chisq.test(table(merged_data$Cluster, merged_data$REGION.x))
```


```{r}
print(chi_test)
```

```{r}
#Normalization to 3NF:
colnames(merged_data)
library(dplyr)
#Structuring the Data into Separate Tables (for 2NF):
# Demographic Data Table (District as Primary Key)
district_data <- merged_data %>%
  select(District, Total.population, Male, Female, Divorces)

# Housing Data Table (District as Foreign Key)
housing_data <- merged_data %>%
  select(District, Housing_Price, Total_Parking)

# School Data Table (District as Foreign Key)
school_data <- merged_data %>%
  select(District, Avg_SCHOOL_LEVEL_RANK, Avg_TOTAL_RANK)

# Traffic Data Table (District as Foreign Key)
traffic_data <- merged_data %>%
  select(District, Hong.Kong.Residents, Mainland.Visitors)
```

```{r}
###Create the Scoring System:
# Min-Max scaling function to scale values between 0 and 10
normalize_score <- function(x) {
  return (10 * (x - min(x)) / (max(x) - min(x)))
}

# Score each characteristic
merged_data$Housing_Price_Score <- normalize_score(merged_data$Housing_Price)
merged_data$Avg_School_Rank_Score <- 10 - normalize_score(merged_data$Avg_SCHOOL_LEVEL_RANK)  # Higher rank gets higher score
merged_data$Total_Parking_Score <- normalize_score(merged_data$Total_Parking)
merged_data$Post_Secondary_Percentage_Score <- normalize_score(merged_data$Post_Secondary_Percentage)
merged_data$Divorces_Score <- normalize_score(merged_data$Divorces)
merged_data$Total_Residents_Score <- normalize_score(merged_data$Hong.Kong.Residents)
merged_data$Total_Visitors_Score <- normalize_score(merged_data$Mainland.Visitors)

# Combine scores for each district
merged_data$Total_Score <- rowSums(merged_data[c("Housing_Price_Score", "Avg_School_Rank_Score", "Total_Parking_Score", 
                                                 "Post_Secondary_Percentage_Score", "Divorces_Score", "Total_Residents_Score", 
                                                 "Total_Visitors_Score")])

# Normalize the total score (if necessary)
merged_data$Total_Score <- normalize_score(merged_data$Total_Score)
# Sort districts by Total_Score and display the top 3
top_districts <- merged_data %>%
  arrange(desc(Total_Score)) %>%
  head(3)
```
```{r}
# Display the top 3 districts along with their REGION (NTE or NTW)
top_districts <- top_districts[, c("District", "Total_Score", "REGION.x")]

```


```{r}
# Visualization of the top 3 districts, including region
ggplot(top_districts, aes(x = reorder(District, Total_Score), y = Total_Score, fill = REGION.x)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("NTE" = "lightgreen", "NTW" = "lightblue")) + # Custom colors for NTE and NTW
  theme_minimal() +
  labs(title = "Top 3 Districts by Total Score", x = "District", y = "Total Score", fill = "Region") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# Print the result
print(top_districts)
```

